### 2020-01-31 README.Rmd
trying to fix binder

[![Travis-CI Build Status](https://travis-ci.org/danielpearson90/vmacfeaturesearch.svg?branch=master)](https://travis-ci.org/danielpearson90/vmacfeaturesearch) [![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/danielpearson90/vmacfeaturesearch/master/?urlpath=rstudio)

>>>>

<!-- badges: start -->
[![Travis-CI Build Status](https://travis-ci.org/danielpearson90/vmacfeaturesearch.svg?branch=master)](https://travis-ci.org/danielpearson90/vmacfeaturesearch) 
[![Launch Rstudio Binder](http://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/danielpearson90/vmacfeaturesearch/master?urlpath=rstudio)
<!-- badges: end -->
